Joint maximum-likelihood of phylogeny and ancestral states is not consistent

### 2018-10-03 joint_inf.tex
pass thru

In words, the joint estimation procedure never recovers the true generating $t^*$ almost everywhere in the space of generating parameters.
This is apparent given Table~\ref{tab:gen-sitepatprob}, as the solution $\hat{t}$ is a linear combination of $p_{\siteSplit_j}$ values, and no generating probability contains an $x^*$ or $y^*$ term.
We may have special cases where certain $x^*$ and $y^*$ values yield consistent estimates for $\hat{t}$, but consistency does not hold in general.
We give an example in the Appendix following the proof of Theorem~\ref{thm:bl_theorem}.
Thus, inconsistency is guaranteed for almost all $x^*$ and $y^*$, though not all $x^*$ and $y^*$.

>>>>

In words, the joint estimation procedure never recovers the true generating $t^*$ almost everywhere in the space of generating parameters.
This is apparent given Table~\ref{tab:gen-sitepatprob}, as the solution $\hat{t}$ is a linear combination of $p_{\siteSplit_j}$ values, and no generating probability contains an $x^*$ or $y^*$ term.
We may have special cases where certain $x^*$ and $y^*$ values yield consistent estimates for $\hat{t}$, but consistency does not hold in general.
We give an example of consistency in a degenerate case in the Appendix following the proof of Theorem~\ref{thm:bl_theorem}.
